Need Fulfillment During Intergroup Contact: Three Experience Sampling Studies

### 2023-05-30 Methods-and-Results.Rmd
tbl reduced

```{r workerVarDescr, include=FALSE}
workerMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType,
    id = "PID",
    selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "interaction_quality", "thermometerDutch_1"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
  )

@@

```{r workerOutVarDescr, include=FALSE}
workerOutMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "interaction_quality", "thermometerDutch_1"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
  )

@@

```{r studentVarDescr, include=FALSE}
studentMlCor <-
  MlCorMat(
    data = dtStudentSupp$studentInteractionType,
    id = "PID",
    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
  )

@@

```{r studentOutVarDescr, include=FALSE}
studentOutMlCor <-
  MlCorMat(
    data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
  )

@@

```{r medicalVarDescr, include=FALSE}
medicalMlCor <-
  MlCorMat(
    data = dtMedical$full,
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "interaction_quality", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
  )

@@

```{r medicalOutVarDescr, include=FALSE}
medicalOutMlCor <-
  MlCorMat(
    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "interaction_quality", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
  )

@@

mdlTblGeneralLong <- 
  rbind(mdlTblGeneralLmer %>%
                             filter(
                               coef %in% c(
                                 "(Intercept)",
                                 "OutgroupInteraction",
                                 "NonOutgroupInteraction",
                                 "OutgroupInteractionM",
                                 "NonOutgroupInteractionM",
                                 "R2Marg_R2Cond"
                               )
                             ),
        mdlTblGeneralLmAll %>%
                             filter(
                               coef %in% c(
                                 "(Intercept)",
                                 "AvQualityCombOut",
                                 "AvQualityComb",
                                 "studyNum1",
                                 "studyNum3",
                                 "SumContactNL:AvQualityCombOut",
                                 "SumContactNL:studyNum1",
                                 "SumContactNL:studyNum3", 
                                 "AvQualityCombOut:studyNum1",
                                 "AvQualityCombOut:studyNum3",
                                 "R2_R2_adjusted"
                               )
                             ) %>%
          mutate(
            B.1 = "",
            ES.1 = "",
            B.2 = "",
            ES.2 =  ""
          )
                           )
mdlTblGeneralLong$coef <- mapvalues(
  mdlTblGeneralLong$coef,
  from = c(
    "R2_R2_adjusted",
    "R2Marg_R2Cond"
  ),
  to = c(
    "$R^2 / R^2_{adjusted}$",
    "$R^2_{marginal} / R^2_{conditional}$"
  )
)

@@

```{r descrFullLong, include=FALSE}
allMlCor <-
  MlCorMat(
    data = dtAll$mlAll, #%>% filter(OutgroupInteraction == "Yes"),
    id = "ID",
    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "qualityOverall", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
  )

@@

```{r descrOutWide, include=FALSE}
allOutMlCor <-
  MlCorMat(
    data = dtAll$mlAll %>% filter(OutgroupInteraction == "Yes"),
    id = "ID",
    selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "qualityOverall", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
  )

>>>>

```{r workerVarDescr, include=FALSE}
workerMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType,
    id = "PID",
    # selection = c("keyMotiveFulfilled", "competence.daily.all", "autonomy.daily.all", "relatedness.daily.all", "interaction_quality", "thermometerDutch_1"),
    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
    selection = c("keyMotiveFulfilled", "interaction_quality", "thermometerDutch_1"),
    labels = c("Core Need", "Quality", "Attitudes NL")
  )

@@

```{r workerOutVarDescr, include=FALSE}
workerOutMlCor <-
  MlCorMat(
    data = dtWorkerSupp$workerInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    # selection = c("keymotive_fulfillemt_1", "competence_1", "autonomy_1", "relatedness_1", "interaction_quality", "thermometerDutch_1"),
    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
    selection = c("keymotive_fulfillemt_1", "interaction_quality", "thermometerDutch_1"),
    labels = c("Core Need", "Quality", "Attitudes NL")
  )

@@

```{r studentVarDescr, include=FALSE}
studentMlCor <-
  MlCorMat(
    data = dtStudentSupp$studentInteractionType,
    id = "PID",
    # selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
    selection = c("KeyNeedFullfillment", "interaction_quality", "AttitudesDutch"),
    labels = c("Core Need", "Competence", "Quality", "Attitudes NL")
  )

@@

```{r studentOutVarDescr, include=FALSE}
studentOutMlCor <-
  MlCorMat(
    data = dtStudentSupp$studentInteractionType %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    # selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "interaction_quality", "AttitudesDutch"),
    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
    selection = c("KeyNeedFullfillment", "interaction_quality", "AttitudesDutch"),
    labels = c("Core Need", "Quality", "Attitudes NL")
  )

@@

```{r medicalVarDescr, include=FALSE}
medicalMlCor <-
  MlCorMat(
    data = dtMedical$full,
    id = "PID",
    # selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "interaction_quality", "AttitudesDutch"),
    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
    selection = c("KeyNeedFulfillment", "AllportsCondition", "interaction_quality", "AttitudesDutch"),
    labels = c("Core Need", "Allport", "Quality", "Attitudes NL")
  )

@@

```{r medicalOutVarDescr, include=FALSE}
medicalOutMlCor <-
  MlCorMat(
    data = dtMedical$full %>% filter(OutgroupInteraction == "Yes"),
    id = "PID",
    # selection = c("KeyNeedFulfillment", "Competence", "Autonomy", "Relatedness", "AllportsCondition", "interaction_quality", "AttitudesDutch"),
    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Allport", "Quality", "Attitudes NL")
    selection = c("KeyNeedFulfillment", "AllportsCondition", "interaction_quality", "AttitudesDutch"),
    labels = c("Core Need", "Allport", "Quality", "Attitudes NL")
  )

@@

mdlTblGeneralLong <- 
  rbind(mdlTblGeneralLmer %>%
                             filter(
                               coef %in% c(
                                 "(Intercept)",
                                 "OutgroupInteraction",
                                 "NonOutgroupInteraction",
                                 "OutgroupInteractionM",
                                 "NonOutgroupInteractionM",
                                 "R2Marg_R2Cond"
                               )
                             ),
        mdlTblGeneralLmAll %>%
                             filter(
                               coef %in% c(
                                 "(Intercept)",
                                 "SumContactNL",
                                 "AvQualityCombOut",
                                 "studyNum1",
                                 "studyNum3",
                                 "SumContactNL:AvQualityCombOut",
                                 "SumContactNL:studyNum1",
                                 "SumContactNL:studyNum3", 
                                 "AvQualityCombOut:studyNum1",
                                 "AvQualityCombOut:studyNum3",
                                 "R2_R2_adjusted"
                               )
                             ) %>%
          mutate(
            B.1 = "",
            ES.1 = "",
            B.2 = "",
            ES.2 =  ""
          )
                           )
mdlTblGeneralLong$coef <- mapvalues(
  mdlTblGeneralLong$coef,
  from = c(
    "R2_R2_adjusted",
    "R2Marg_R2Cond"
  ),
  to = c(
    "$R^2 / R^2_{adjusted}$",
    "$R^2_{marginal} / R^2_{conditional}$"
  )
)

@@

```{r descrFullLong, include=FALSE}
allMlCor <-
  MlCorMat(
    data = dtAll$mlAll, #%>% filter(OutgroupInteraction == "Yes"),
    id = "ID",
    # selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "qualityOverall", "AttitudesDutch"),
    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
    selection = c("KeyNeedFullfillment", "qualityOverall", "AttitudesDutch"),
    labels = c("Core Need", "Quality", "Attitudes NL")
  )

@@

```{r descrOutWide, include=FALSE}
allOutMlCor <-
  MlCorMat(
    data = dtAll$mlAll %>% filter(OutgroupInteraction == "Yes"),
    id = "ID",
    # selection = c("KeyNeedFullfillment", "Competence", "Autonomy", "Relatedness", "qualityOverall", "AttitudesDutch"),
    # labels = c("Core Need", "Competence", "Autonomy", "Relatedness", "Quality", "Attitudes NL")
    selection = c("KeyNeedFullfillment", "qualityOverall", "AttitudesDutch"),
    labels = c("Core Need", "Quality", "Attitudes NL")
  )
